---
title: " "
output:
   html_document:
     css: style.css
---



```{r, include = FALSE}

knitr::opts_chunk$set(fig.width = 7, fig.height = 7, collapse = TRUE, dpi = 300, warning = FALSE, message = FALSE, comment = " ")

```


<p align = "justify">
<font size="4"> **Library** </font>
</p>

```{r}

library(AICcmodavg)
library(ape)
library(caper)
library(geiger)
library(kableExtra)
library(MuMIn)
library(nlme)
library(phytools)
library(plotrix)
library(shape)
library(car)
library(magick)

```

<p align = "justify">
<font size="4"> **Session information** </font>
</p>


```{r, warning = FALSE, comment = " "}

R.version
sessionInfo()

```

```{r, include = FALSE}


evo_bd <- read.csv("evo_body_size_mass2.csv", row.names = 1)
evo_bd <- evo_bd[evo_bd$diet != "Herbivorous", ]
evo_bd <- evo_bd[evo_bd$Family != "Sphenodontidae", ]
tree <- read.nexus("time.tree.nex")
str(evo_bd)



## Scaled mass index for females

par(mar = c(6, 6, 1, 1), mgp = c(4, 1, 0))
plot(rawFem ~ female.SVL, data = evo_bd, ylab = "Female mass (g)", xlab = "Female length (mm)", las = 1)

par(mar = c(5.1, 4.1, 4.1, 2.1), mgp = c(3, 1, 0))
plot(log(rawFem) ~ log(female.SVL), data = evo_bd, ylab = "Female mass ln(g)", xlab = "Female length ln(mm)", las = 1)
step1 <- lm(log(rawFem) ~ log(female.SVL), data = evo_bd)
summary(step1)

L0 <- mean(evo_bd$female.SVL)
Mi <- evo_bd$rawFem
Li <- evo_bd$female.SVL

evo_bd$M_females <- Mi*(L0/Li)^3


## Scaled mass index for hatchlings

plot(rawHatc ~ hatchling.neonate.SVL, data = evo_bd, ylab = "Hatchling mass (g)", xlab = "Hatchling length (mm)", las = 1)

plot(log(rawHatc) ~ log(hatchling.neonate.SVL), data = evo_bd, ylab = "Hatchling mass log(g)", xlab = "Hatchling length log(mm)", las = 1)
step1h <- lm(log(rawHatc) ~ log(hatchling.neonate.SVL), data = evo_bd)
summary(step1h)

L0h <- mean(evo_bd$hatchling.neonate.SVL)
Mih <- evo_bd$rawHatc
Lih <- evo_bd$hatchling.neonate.SVL

evo_bd$M_hatchlings <- Mih*(L0h/Lih)^2.8
head(evo_bd)


check <- name.check(tree, evo_bd)
rm_phy <- check$tree_not_data
rm_dat <- check$data_not_tree
ctree <- drop.tip(tree, rm_phy)

cdat <- subset(evo_bd, subset = evo_bd$Binomial %in% ctree$tip, select = names(evo_bd)[1:27])
name.check(ctree, cdat)


## Mean clutch size

cdat$mclutch <- (cdat$smallest.mean.clutch.size + cdat$largest.mean.clutch.size) / 2


## Reproductive output

cdat$rep_out <- (cdat$mclutch * cdat$M_hatchlings)
str(cdat)

tapply(cdat$M_females, cdat$Family, length)



```


```{r, include = FALSE}


## Lacertilia

cdat$foraging.mode <- factor(cdat$foraging.mode, levels = c("widely foraging", "sit and wait", "mixed")) ## I am changing the order of the levels here so that the contrast of the coefficients can be made against the level "widely foraging".


## Standardized mass, M.

dat_full <- cdat

check_full <- name.check(tree, dat_full)
rm_phy_full <- check_full$tree_not_data
rm_dat_full <- check_full$data_not_tree
ctree_full <- drop.tip(tree, rm_phy_full)
name.check(ctree_full, dat_full)


## Number of individuals in each category (foraging mode)

tapply(dat_full$M_females, dat_full$foraging.mode, length)

## Mean scaled mass index per category

tapply(dat_full$M_females, dat_full$foraging.mode, mean)

## Mean reproductive output per category

tapply(dat_full$rep_out, dat_full$foraging.mode, mean)


full_mod <- gls(rep_out ~ M_females*foraging.mode, correlation = corBrownian(phy = ctree_full, form = ~Binomial), data = dat_full, method = "ML")
summary(full_mod)


full_mod1 <- gls(rep_out ~ M_females + foraging.mode, correlation = corBrownian(phy = ctree_full, form = ~Binomial), data = dat_full, method = "ML")
summary(full_mod1)


full_mod2 <- gls(rep_out ~ M_females*foraging.mode, correlation = corPagel(value = 0, phy = ctree_full, form = ~Binomial), data = dat_full, method = "ML")
summary(full_mod2)

full_mod3 <- gls(rep_out ~ M_females + foraging.mode, correlation = corPagel(value = 0, phy = ctree_full, form = ~Binomial), data = dat_full, method = "ML")
summary(full_mod3)

```



<p align = "justify">
<font size="4"> **Consider only sit-and-wait and widely-foraging lizards** </font>
</p>

<p align = "justify">
<font size="4">Almost a year ago, my mentors and I submitted a paper to *Proceedings of the Royal Society B*. In this paper, we investigated the relationship between foraging behavior and reproducitve effort in lizards (see [here](https://royalsocietypublishing.org/doi/10.1098/rspb.2022.0180)). One of the most important comments I got from a reviwer was related to the scatter in the data. The reviwer stated that the variance of the data was very large, preventing us from making robust conclusions. In response to this concern, I would like to show here one way to deal with this issue: <br><br> As observed in figure 3a-b of the paper, the majority of the species are clustered at small sizes along the x-axis, while a few others are grouped at large sizes and seem to be "extreme cases". Some of the latter cases are "mixed-foraging" species that can behave either as a "widely-foraging" or "sit-and-wait" species. If I remove the "mixed" category and make the species behave randomly as "widely foragers" or "sit-and-wait forager", I could recalculate the significance of the interaction to determine whether the results hold or not. If I do so multiple time (>1000), I can calculate the proportion of time that "widely-foraging" species have greater reproductive output than "sit-and-wait" species, as indicated by the original results. Let's do it: </font>
</p>


```{r, eval = FALSE}

## Considering only sit-and-wait and widely-foraging lizards


set.seed(94)

options(scipen = 999)

active <- dat_full[dat_full$foraging.mode == "widely foraging",  ]
ambush <- dat_full[dat_full$foraging.mode == "sit and wait",  ]
mixed <- dat_full[dat_full$foraging.mode == "mixed",  ]

savep <- rep(NA, 1000)
savei <- rep(NA, 1000)

for(i in 1:1000){
    
    randomizing <- sample(rep(c("widely foraging", "sit and wait"), each = length(mixed$foraging.mode)), size = length(mixed$foraging.mode))
    mixed$foraging.mode <- randomizing
    merg <- rbind(active, ambush, mixed)

    ## model
    mod <- gls(rep_out ~ M_females*foraging.mode, correlation = corPagel(value = 0, phy = ctree_full, form = ~Binomial), data = merg, method = "ML")

    ## Confidence intervals

    ## sit and wait

    sw <- merg[merg$foraging.mode == "sit and wait", ]
    check_sw <- name.check(tree, sw)
    rm_phy_sw <- check_sw$tree_not_data
    rm_dat_sw <- check_sw$data_not_tree
    ctree_sw <- drop.tip(tree, rm_phy_sw)

    SSX.sw <- sum(round((sw$M_females - mean(sw$M_females))^2), 2)
    s2.sw <- var(sw$rep_out)
    n.sw <- length(sw$rep_out)
    x.sw <- seq(min(sw$M_females), max(sw$M_females), 0.5)
    m.x.sw <- mean(round(sw$M_females, 1))
    se.sw <- sqrt(s2.sw*((1/n.sw) + (((x.sw - m.x.sw)^2)/SSX.sw)))
    is.sw <- qt(0.975, df = n.sw - 2)
    ii.sw <- qt(0.025, df = n.sw - 2)
    ic.s.sw <- se.sw*is.sw
    ic.i.sw <- se.sw*ii.sw
    upper.i.sw <- ((coef(mod)[1] + coef(mod)[3]) + (coef(mod)[2] + coef(mod)[4])*x.sw) + ic.s.sw
    lower.i.sw <- ((coef(mod)[1] + coef(mod)[3]) + (coef(mod)[2] + coef(mod)[4])*x.sw) + ic.i.sw


    ## widely foraging

    wf <- merg[merg$foraging.mode == "widely foraging", ]
    check_wf <- name.check(tree, wf)
    rm_phy_wf <- check_wf$tree_not_data
    rm_dat_wf <- check_wf$data_not_tree
    ctree_wf <- drop.tip(tree, rm_phy_wf)

    SSX.wf <- sum(round((wf$M_females - mean(wf$M_females))^2), 2)
    s2.wf <- var(wf$rep_out)
    n.wf <- length(wf$rep_out)
    x.wf <- seq(min(wf$M_females), max(wf$M_females), 0.5)
    m.x.wf <- mean(round(wf$M_females,1))
    se.wf <- sqrt(s2.wf*((1/n.wf) + (((x.wf - m.x.wf)^2)/SSX.wf)))
    is.wf <- qt(0.975, df = n.wf - 2)
    ii.wf <- qt(0.025, df = n.wf - 2)
    ic.s.wf <- se.wf*is.wf
    ic.i.wf <- se.wf*ii.wf
    upper.i <- (coef(mod)[1] + coef(mod)[2]*x.wf) + ic.s.wf
    lower.i <- (coef(mod)[1] + coef(mod)[2]*x.wf) + ic.i.wf

    png(paste("figure", i, ".png", sep = ""), width = 7, height = 7, units = "in", res = 300)
    plot(merg$rep_out ~ merg$M_females, type = "p", xlab = " ", ylab = "Hatchling mass x clutch size (g)", cex.lab = 1.2, pch = 21, bg = c("purple", "skyblue")[as.numeric(merg$foraging.mode)], col = c("purple", "skyblue")[as.numeric(merg$foraging.mode)], las = 1)
    polygon(c(rev(x.sw), x.sw), c(rev(lower.i.sw), upper.i.sw), border = FALSE, col = rgb(0, 0, 1, alpha = 0.2))
    lines(x = x.sw, y = ((coef(mod)[1] + coef(mod)[3]) + (coef(mod)[2] + coef(mod)[4])*x.sw), col = "skyblue", lwd = 2)

    polygon(c(rev(x.wf), x.wf), c(rev(lower.i), upper.i), border = FALSE, col = rgb(0.8, 0, 0.7, alpha = 0.3))
    lines(x = x.wf, y = coef(mod)[1] + coef(mod)[2]*x.wf, col = "purple", lwd = 2)

    text(x = 7.7, y = 30, substitute(paste(italic("Interaction \n "))), family = "serif")
    text(x = 7.7, y = 30, round(coef(mod)[4], 3), family = "serif")
    text(x = 7.7, y = 27, paste("p = ", round(anova(mod)[4, 3], 3), sep = " "), family = "serif")

    mtext(expression(hat(M) (g)), side = 1, line = 4, cex = 1)
    legend("topleft", legend = c("sit-and-wait foraging", "widely foraging"), lty = 1, bty = "n", pch = c(16, 16), bg = c("black", "black"), col = c("skyblue", "purple"), cex = 1)
    
    dev.off()
    
    
    savep[i] <- round(anova(mod)[4, 3], 3)
    savei[i] <- round(coef(mod)[4], 3)

}
    



## Estimate proportion of time that the p-value of the interaction was significant

mean(savep < 0.05)


```

```{r, echo = FALSE}

print("0.574")

```


```{r, eval = FALSE}

## Mean affect size of the interaction

mean(savei)


```

```{r, echo = FALSE}


print("-0.259")

```


```{r}

## list file names and read in

imgs <- list.files(path = "/Users/dpadil10/Dropbox (ASU)/gif/gif/", full.names = TRUE)
img_list <- lapply(imgs, image_read)

## join the images together
img_joined <- image_join(img_list)

## animate at 2 frames per second
img_animated <- image_animate(img_joined, fps = 2)

img_animated

```


